Understanding the Lomb-Scargle Periodogram

### 2017-01-06 PracticalLombScargle.tex
Add section on extensions

All figures in this work were produced using Python, and in particular the
Numpy \citep{numpy},
Pandas \citep{pandas},
Astropy \citep{Astropy2013},
and Matplotlib \citep{matplotlib} packages.
Code to reproduce these figures is available in IPython notebooks at \url{http://github.com/jakevdp/PracticalLombScargle/}.

@@

In the scientific literature it is quite common to come across various proposals
for a Nyquist-like or pseudo-Nyquist limit in the case of irregular sampling.
A few typical approaches include using the mean of the sampling intervals
\citep[e.g.][]{Scargle82, Horne86, NumRec},
the harmonic mean of the sampling intervals \citep[e.g.][]{Debosscher07},
or the minimum sample spacing \citep[e.g.][]{Percy86, Roberts87, Press89, Hilditch01}.
All of these are tempting criteria in that they recover the classical Nyquist 
frequency in the limit of evenly-spaced data.
Unfortunately, none of these approaches is correct: in general,
unevenly-sampled data can probe frequencies far larger than any of these
supposed limits (a fact that some of these citations do hint at
parenthetically).

@@

While Nyquist arguments based on average or minimum sampling fail spectacularly,
there is a sense in which the Nyquist limit can be applied to unevenly-spaced
data. \citet{Eyer99} explores this issue in some detail, and in particular
proves the following:
\begin{quote}
Let $p$ be the largest value such that each $t_i$ can be written $t_i = t_0 + n_i p$, for integers $n_i$. The Nyquist Frequency then is $f_{Ny} = 1 / (2p)$.
\end{quote}
In other words, computing the Nyquist rate for unevenly-spaced data requires
finding some common factor, such that each spacing $\Delta t_i$ is {\it exactly}
an integer multiple of this factor.
This can be proven formally, but can be understood by thinking of such data as
a windowed version of uniformly sampled data with spacing $p$.
Such uniform data has a classical Nyquist limit of $1/(2p)$, and a window function applied to that data does not change that fact.

\Fig{nyquist-eyer99} shows an example of such a Nyquist frequency.
The data are non-uniformly sampled at times $t_i = n_i * p$, with $p=0.01$.
This results in a Nyquist frequency $f_{Ny} = 50$, and we see the expected
behavior beyond this frequency: the signal at $f > f_{Ny}$ consists of repeated
aliases of the signal at $f < f_{Ny}$.

@@

Keep in mind that the windowing limit $f_{max}$ is quite different than a
Nyquist limit: the Nyquist limit is the frequency beyond which all signal
is aliased into the Nyquist range; the windowing limit is the frequency
beyond which all signal is zero.

@@

Thus the strong spike at a period of 1 day indicate that observations are
taken near the same time of day: this is typical of a ground-based survey
which observes only at night.
The additional spikes at periods of $1/n$ days (for integer $n$) are aliases
of this same effect.

@@

This behavior is illustrated in \fig{LINEAR-window-effect}.
The upper panel shows the window power spectrum as a function of frequency, while lower panel shows the observed signal power spectrum as a function of frequency.
As noted in the discussion of \fig{LINEAR-window}, the window function shows a strong signal at frequencies corresponding to 1 day and 1 year; the latter can be seen in the inset plot.
The power at both these scales is clearly imprinted on the observed power spectrum, as shown in the lower panel and its inset.
This imperfect aliasing is similar to the perfect aliasing seen in regularly-sampled data at the Nyquist frequency; however, in this case the magnitude of the
aliased signal fades further from the frequency driving the signal.

@@

\begin{figure}[ht]
  \centering
  \includegraphics[width=\textwidth]{fig16_kepler_data}
  \caption{An RR Lyrae variable observed by the Kepler project \citep[see][]{Kolenberg2010}.
    {\it upper left:} the 4083 observed fluxes over roughly three months.
    {\it upper right:} the window power spectrum, which is quite close to that of regularly-spaced data with a cadence of 29.4 minutes.
    {\it lower left:} the time between observations. other than missing measurements, the spacing between observations is nearly uniform. the lower panel gives a closer look at the majority of the spacings, which are not exactly the same but rather span a range of $\pm 50$ms around the main period observed in the window function.
    {\it lower right:} the data power spectrum, showing approximate aliasing and clearly indicating a peak near a period of 13.6 hours, along with higher-order components at multiples of this value.
    \figlabel{kepler-data}}
\end{figure}

Space-based missions often have quite different observing windows.
For example, the upper-left panel of \fig{kepler-data}
shows observations of an RR-Lyrae variable star from the Kepler survey,
measured over 4000 times over a period of three months,
with an irregular observing cadence of just under 30 minutes
 \citep[For deeper discussion of these observations, see][]{Kolenberg2010}.
The Kepler observations are very nearly uniformly-spaced, and this is reflected
in the window power spectrum, shown in the upper-right panel of
\fig{kepler-data}.
The window function is a series of very narrow evenly-spaced spikes,
reminiscent of the Dirac comb shown in \figs{comb-window-1}{comb-window-2},
which we used to motivate the idea of the Nyquist limit.
Thus, in this case we can treat $f_{Ny} = 0.5/29.4$ minutes$^{-1}$ as the
effective Nyquist limit for the data, though aliasing is imperfect due to
the uneven spacing of samples, shown in the lower-left panels of
\fig{kepler-data}.

@@

Up until now, we've been mainly discussing the direct extension of the Schuster
periodogram in \eq{schuster-periodogram} to non-uniform data.
Returning to this definition, we can rewrite the expression in a more
suggestive way:
\begin{eqnarray}
  P(f)
  &=& \frac{1}{N}\left|\sum_{n=1}^N g(t_n)e^{-2\pi i t_n} \right|^2 \nonumber\\
  &=& \frac{1}{N}\left[
    \left(\sum_n g_n \cos(2\pi f t_n)\right)^2
    + \left(\sum_n g_n \sin(2\pi f t_n)\right)^2
    \right]
  \eqlabel{classical-periodogram}
\end{eqnarray}
Although this form of the non-uniform periodogram can be useful for identifying
periodic signals, its statistical properties are not as straightforward as in
the uniform case.
In this case, when we say an estimator with ``good statistical properties'',
we mean that when it is applied to data with straightforward, uncorrelated
noise, the result is a periodogram estimate in which the noise is also
straightforward and uncorrelated.

\citet{Scargle82} showed that while the classical periodogram of
\eq{classical-periodogram} has these desireable statistical properties
in the case of uniform sampling, this does not hold for
\eq{classical-periodogram} when the sampling becomes non-uniform.
To address this, he considered a generalized form of the periodogram,
\begin{equation}
  P(f) = \frac{A^2}{2}\left(\sum_n g_n \cos(2\pi f [t_n-\tau])\right)^2
       + \frac{B^2}{2} \left(\sum_n g_n \sin(2\pi f [t_n-\tau])\right)^2,
\end{equation}
where $A$ and $B$ are arbitrary functions of the frequency $f$ and
observing times $\{t_i\}$ (but not the values $\{g_n\}$, and showed
that you can choose one particular form of $A$ and $B$ such that
\begin{enumerate}
  \item The periodogram reduces to the classical form in the case of equally-spaced data,
  \item The periodogram has desireable statistical properties, in the sense discussed above,
  \item The periodogram is insensitive to global time-shifts in the data.
\end{enumerate}
The values of $A$ and $B$ leading to these properties lead to the following
modification of the classical expression for the periodogram:
\begin{eqnarray}
  P(f) =
  \frac{1}{2} \Bigg\{ &
  \bigg(\sum_n g_n \cos(2\pi f [t_n-\tau])\bigg)^2 \bigg/
  \sum_n \cos^2(2\pi f [t_n-\tau]) &\nonumber\\
  & + ~ \bigg(\sum_n g_n \sin(2\pi f [t_n-\tau])\bigg)^2 \bigg/
  \sum_n \sin^2(2\pi f [t_n-\tau]) & \Bigg\}
  \eqlabel{lomb-scargle-periodogram}
\end{eqnarray}
where $\tau$ is specified for each $f$ to ensure time-shift invariance:
\begin{equation}
  \tau = \frac{1}{4\pi f}\tan^{-1}\Bigg(
  \frac{\sum_n \sin(4\pi f t_n)}{\sum_n \cos(4\pi f t_n)}\Bigg).
  \eqlabel{tau-def}
\end{equation}
This modified periodogram differs from the classical periodogram only to
the extent that the denominators $\sum_n \sin^2(2\pi f t_n)$ and
$\sum_n \cos^2(2\pi f t_n)$ differ from $N/2$, which is the expected value of
each of these quantities in the limit of complete phase sampling at each
frequency.
Thus, in many cases of interest the Lomb-Scargle periodogram only differs
slightly from the classical/Schuster periodogram; an example of this is seen
in \fig{ls-comparison}.

@@

\subsection{Data Centering and the Floating Mean Periodogram}
\sectlabel{centering-data}

Another commonly-applied modification of the periodogram has variously been
called the {\it Date-compensated Discrete Fourier Transform} \citep{Ferraz-Mello81}, the {\it floating-mean periodogram} \citep{Cumming99}, and the {\it generalized Lomb-Scargle Method} \citep{Zechmeister09}, and involves adding an offset term to the sinusoidal model at each frequency:
\begin{equation}
  y_{model}(t;f) = y_{0, f} + A_f \sin(2 \pi f (t - \phi_f))
  \eqlabel{floating-mean-model}
\end{equation}
This is important, because the standard Lomb-Scargle approach assumes that the
data are pre-centered around the mean value of the signal.
In the past this was primarily accomplished by pre-centering the data before
the Lomb-Scargle fit using the mean estimated from the data points themselves.

@@

\subsection{Higher-order Fourier Models}

@@

This background noise can also be understood in terms of aliasing.
Consider \fig{kepler-multiterm}, which shows several multi-term fits to the
data from \fig{kepler-data}.
Given a standard periodogram peak at $f_0$, a 2-term periodogram will have an
additional peak at $f_0 / 2$, in which the original peak is the second
harmonic. Similarly, a 3-term periodogram will add additional peaks both at
$f_0 / 2$ and $f_0 / 3$, due to the original peak falling in the second and
third harmonic.

@@

In cases where the single-term power spectrum is itself very noisy, these
additional aliases can quickly wash-out any gains from the more complicated
model.
Consider \fig{LINEAR-multiterm}, in which the $n=3$ model leads to very large
noise at the low-frequency end. In this case, spurious periodogram peaks due
to coincidences of such aliases may become problematic for even moderately
noisy models.

@@

Fortunately, several faster implementations have been proposed to compute the
periodogram to arbitrary precision in $\mathcal{O}(N\log N)$ time.
The first of these is discussed in \citet{Press89}, which uses an inverse
interpolation operation along with a Fast Fourier Transform to compute the
trigonometric components of \eq{lomb-scargle-periodogram} very efficiently over
a large number of frequencies.
A qualitatively similar approach is presented by \citet{Leroy2012},
and makes use of the Non-equispaced Fast Fourier Transform
\citep[NFFT, see][]{Keiner2009} to compute the Lomb-Scargle periodogram about
a factor of 10 faster than the \citet{Press89} approach.
All periodograms in this paper were computed using the Astropy
implementation of the \citet{Press89} algorithm, which was adapted from Python
code released to accompany \citet{VanderPlas2015}.

\todo{Reference fast chi-square approach}

>>>>

All figures in this work were produced using Python, and in particular the
Numpy \citep{numpy, numpybook},
Pandas \citep{pandas},
Astropy \citep{Astropy2013},
and Matplotlib \citep{matplotlib} packages.
Code to reproduce these figures is available in IPython notebooks at \url{http://github.com/jakevdp/PracticalLombScargle/}.

@@

In the scientific literature it is quite common to come across various proposals
for a Nyquist-like or pseudo-Nyquist limit in the case of irregular sampling.
A few typical approaches include using the mean of the sampling intervals
\citep[e.g.][]{Scargle82, Horne86, NumRec},
the harmonic mean of the sampling intervals \citep[e.g.][]{Debosscher07},
or the minimum sample spacing \citep[e.g.][]{Percy86, Roberts87, Press89, Hilditch01}.
All of these are tempting criteria in that they recover the classical Nyquist 
frequency in the limit of evenly-spaced data.
Unfortunately, none of these approaches is correct: in general,
unevenly-sampled data can probe frequencies far larger than any of these
supposed limits (a fact that several of these citations do hint at
parenthetically).

@@

While Nyquist arguments based on average or minimum sampling fail spectacularly,
there is a sense in which the Nyquist limit can be applied to unevenly-spaced
data. \citet{Eyer99} explore this issue in some detail, and in particular
proves the following:
\begin{quote}
Let $p$ be the largest value such that each $t_i$ can be written $t_i = t_0 + n_i p$, for integers $n_i$. The Nyquist Frequency then is $f_{Ny} = 1 / (2p)$.
\end{quote}
In other words, computing the Nyquist rate for unevenly-spaced data requires
finding some common factor, such that each spacing $\Delta t_i$ is {\it exactly}
an integer multiple of this factor.
This can be proven formally, but can be understood by thinking of such data as
a windowed version of uniformly sampled data with spacing $p$, where the window
is zero at some observations.
Such uniform data has a classical Nyquist limit of $1/(2p)$, and a window
function applied to that data does not change that fact.

\Fig{nyquist-eyer99} shows an example of such a Nyquist frequency.
The data are non-uniformly sampled at times $t_i = n_i * p$, with $p=0.01$
and $n_i$ drawn randomly from positive integers less than 10,000.
According to the \citet{Eyer99} definition,
this results in a Nyquist frequency $f_{Ny} = 50$, and we see the expected
behavior beyond this frequency: the signal at $f > f_{Ny}$ consists of repeated
aliases of the signal at $f < f_{Ny}$.

@@

Keep in mind that the windowing limit $1/(2\delta t)$ is quite different than a
Nyquist limit: the Nyquist limit is the frequency beyond which all signal
is aliased into the Nyquist range; the windowing limit is the frequency
beyond which all signal is zero or nearly zero.

@@

Thus the strong spike at a period of 1 day indicate that observations are
taken near the same time of day: this is typical of a ground-based survey
with observations recorded only at night.
The additional spikes at periods of $1/n$ days (for integer $n$) are aliases
of this same effect.

@@

This behavior is illustrated in \fig{LINEAR-window-effect}.
The upper panel shows the window power spectrum as a function of frequency (not period, as in \fig{LINEAR-window}), while lower panel shows the observed signal power spectrum as a function of frequency.
The upper panel and its inset show clearly the 1-day and 1-year features we noted previously.
The lower panel shows the observed power spectrum of the data: these diurnal and annual peaks in the window function are quite clearly imprinted on the observed power spectrum at relevant scales.
This approximate aliasing is similar to the exact aliasing seen in regularly-sampled data at the Nyquist frequency; however, in this case the magnitude of the
aliased signal fades further from the frequency driving the signal.

@@

\begin{figure}[ht]
  \centering
  \includegraphics[width=\textwidth]{fig16_kepler_data}
  \caption{An RR Lyrae variable observed by the Kepler project \citep[see][]{Kolenberg2010}.
    {\it upper left:} the 4083 observed fluxes over roughly three months.
    {\it upper right:} the window power spectrum, which is quite close to that of regularly-spaced data with a cadence of 29.4 minutes.
    {\it lower left:} the time between observations. Missing measurements aside, the spacing between observations is nearly uniform. the lower panel gives a closer look at the majority of the spacings, which are not exactly the same but rather span a range of $\pm 50$ms around the 29.4-minute period observed in the window function.
    {\it lower right:} the data power spectrum, showing approximate aliasing and clearly indicating a peak near a period of 13.6 hours, along with higher-order components at multiples of this value.
    \figlabel{kepler-data}}
\end{figure}

Space-based surveys will generally have quite different observing windows.
For example, the upper-left panel of \fig{kepler-data}
shows observations of an RR-Lyrae variable star from the Kepler survey,
measured over 4000 times over a period of three months,
with an irregular observing cadence of just under 30 minutes
 \citep[For deeper discussion of these observations, see][]{Kolenberg2010}.
The Kepler observations are very nearly uniformly-spaced, and this is reflected
in the window power spectrum, shown in the upper-right panel of
\fig{kepler-data}.
The window function is a series of very narrow evenly-spaced spikes,
reminiscent of the Dirac comb shown in \figs{comb-window-1}{comb-window-2},
which we used to motivate the idea of the Nyquist limit.
Thus, in this case we can treat $f_{Ny} = 0.5/29.4$ minutes$^{-1}$ as the
effective Nyquist limit for the data, though aliasing is imperfect due to
the uneven spacing of samples, shown in the lower-left panels of
\fig{kepler-data}.

@@

Up until now, we've been mainly discussing the direct extension of the Schuster
periodogram in \eq{schuster-periodogram} to non-uniform data.
Returning to this definition, we can rewrite the expression in a more
suggestive way:
\begin{eqnarray}
  P(f)
  &=& \frac{1}{N}\left|\sum_{n=1}^N g(t_n)e^{-2\pi i t_n} \right|^2 \nonumber\\
  &=& \frac{1}{N}\left[
    \left(\sum_n g_n \cos(2\pi f t_n)\right)^2
    + \left(\sum_n g_n \sin(2\pi f t_n)\right)^2
    \right]
  \eqlabel{classical-periodogram}
\end{eqnarray}
Although this form of the non-uniform periodogram can be useful for identifying
periodic signals, its statistical properties are not as straightforward as in
the uniform case: the periodogram has noise properties that are nontrivial
to quantify, even when applied to ideal data (data with uncorrelated
Gaussian noise).

For the sake of evaluating the significance of periodogram peaks
(see \sect{uncertainties}), it would be preferable if the non-equispaced
periodogram, had uncertainties that were uncorrelated, and could be
straightforwardly computed from the uncertainties of the data.

\citet{Scargle82} showed that while the classical periodogram of
\eq{classical-periodogram} has such desireable statistical properties
in the case of uniform sampling, this does not hold for
\eq{classical-periodogram} when the sampling becomes non-uniform.
To address this, he considered a generalized form of the periodogram,
\begin{equation}
  P(f) = \frac{A^2}{2}\left(\sum_n g_n \cos(2\pi f [t_n-\tau])\right)^2
       + \frac{B^2}{2} \left(\sum_n g_n \sin(2\pi f [t_n-\tau])\right)^2,
\end{equation}
where $A$ and $B$ are arbitrary functions of the frequency $f$ and
observing times $\{t_i\}$ (but not the values $\{g_n\}$, and showed
that you can choose one particular form of $A$ and $B$ such that
\begin{enumerate}
  \item The periodogram reduces to the classical form in the case of equally-spaced data,
  \item The periodogram has desireable statistical properties, in the sense discussed above,
  \item The periodogram is insensitive to global time-shifts in the data.
\end{enumerate}
The values of $A$ and $B$ leading to these properties lead to the following
modification of the classical expression for the periodogram:
\begin{eqnarray}
  P(f) =
  \frac{1}{2} \Bigg\{ &
  \bigg(\sum_n g_n \cos(2\pi f [t_n-\tau])\bigg)^2 \bigg/
  \sum_n \cos^2(2\pi f [t_n-\tau]) &\nonumber\\
  & + ~ \bigg(\sum_n g_n \sin(2\pi f [t_n-\tau])\bigg)^2 \bigg/
  \sum_n \sin^2(2\pi f [t_n-\tau]) & \Bigg\}
  \eqlabel{lomb-scargle-periodogram}
\end{eqnarray}
where $\tau$ is specified for each $f$ to ensure time-shift invariance:
\begin{equation}
  \tau = \frac{1}{4\pi f}\tan^{-1}\Bigg(
  \frac{\sum_n \sin(4\pi f t_n)}{\sum_n \cos(4\pi f t_n)}\Bigg).
  \eqlabel{tau-def}
\end{equation}
This modified periodogram differs from the classical periodogram only to
the extent that the denominators $\sum_n \sin^2(2\pi f t_n)$ and
$\sum_n \cos^2(2\pi f t_n)$ differ from $N/2$, which is the expected value of
each of these quantities in the limit of complete phase sampling at each
frequency.
Thus, in many cases of interest the Lomb-Scargle periodogram only differs
slightly from the classical/Schuster periodogram; an example of this is seen
in \fig{ls-comparison}.

@@

\subsection{Data Centering and the Floating Mean Periodogram}
\sectlabel{floating-mean}

Another commonly-applied modification of the periodogram has variously been
called the {\it Date-compensated Discrete Fourier Transform} \citep{Ferraz-Mello81}, the {\it floating-mean periodogram} \citep{Cumming99}, and the {\it generalized Lomb-Scargle Method} \citep{Zechmeister09}, and involves adding an offset term to the sinusoidal model at each frequency\footnote{We choose to follow \citet{VanderPlas2015} and call this a ``Floating Mean'' model, to avoid confusion surrounding the different meanings of the term ``generalized periodogram'' in, {e.g.} \citet{Bretthorst88} and \citet{Zechmeister09}.}:
\begin{equation}
  y_{model}(t;f) = y_{0, f} + A_f \sin(2 \pi f (t - \phi_f))
  \eqlabel{floating-mean-model}
\end{equation}

This is important, because the standard Lomb-Scargle approach assumes that the
data are pre-centered around the mean value of the signal.
In the past this was primarily accomplished by pre-centering the data before
the Lomb-Scargle fit using the mean estimated from the data points themselves.

@@

\subsection{Higher-order Fourier Models}
\sectlabel{multiterm}

@@

This background noise can also be understood in terms of aliasing.
Consider \fig{kepler-multiterm}, which shows several multi-term fits to the
Kepler data from \fig{kepler-data}.
Given a standard periodogram peak at $f_0$, a 2-term periodogram will have an
additional peak at $f_0 / 2$, in which the original peak is the second
harmonic. Similarly, a 3-term periodogram will add additional peaks both at
$f_0 / 2$ and $f_0 / 3$, due to the original peak falling in the second and
third harmonic.
In general, you can expect an $N$-term periodogram to contain $N$ copies of
every feature present in the standard periodogram, in addition to any
new or strengthened features due to the more flexible model.

@@

In cases where the single-term power spectrum is itself noisy and/or dominated
by partial aliasing due to window effects, these additional aliases can
quickly wash-out any gains from the more complicated model.
For example, consider the periodogram in \fig{LINEAR-multiterm}: as previously
discussed, this periodogram contains a number of aliases of the true peak due
to the dominant 24-hour signal in the window function.
Adding terms to this model only compounds this problem, increasing the number of
spurious peaks at the low-frequency end.
For data with even moderate levels of noise, coincidences of these peaks can
easily lead to spurious signals dominating the true peak.

\subsection{Additional Extensions}
When the periodogram is viewed from the least-squares model-fitting perspective,
there is no need to limit the analysis to sums of sinusoids.
There have been some very interesting applications extending this type of
analysis to more arbitrary models.
For example, \citet{Bretthorst88} studies ``periodograms'' which measure
decaying signals, non-stationary signals, multiple signals, and other models,
and shows the effectiveness of such approaches in applications from
medical imaging and astronomy.

On the astronomy side, several examples of such analyses exist.
For example, the Supersmoother approach to detecting periodicity
involves fitting a flexible non-parametric smoothing
function to the data at each frequency: the flexibility of the model leads
to fewer issues of aliasing \citep{Reimann94}.
Another approach is to use empirically-derived templates as a functional fit
at each frequency; this has been employed effectively in \citet{Sesar2010,
Sesar2013} and related work.
Finally, there has been some exploration of extensions to the Lomb-Scargle
periodogram for use with multi-band observations, using various forms of
regularization to control model complexity \citep{VanderPlas2015, Long2016}.

\subsection{A Note About ``Bayesian'' Periodograms}

@@

Fortunately, several faster implementations have been proposed to compute the
periodogram to arbitrary precision in $\mathcal{O}(N\log N)$ time.
The first of these is discussed in \citet{Press89}, which uses an inverse
interpolation operation along with a Fast Fourier Transform to compute the
trigonometric components of \eq{lomb-scargle-periodogram} very efficiently over
a large number of frequencies.
\citet{Zechmeister09} showed how this approach can be easily extended to
the floating mean periodogram discussed in \sect{floating-mean}.

A qualitatively similar approach to the \citet{Press89} algorithm
is presented by \citet{Leroy2012}:
It makes use of the Non-equispaced Fast Fourier Transform
\citep[NFFT, see][]{Keiner2009} to compute the Lomb-Scargle periodogram about
a factor of 10 faster than the \citet{Press89} approach.
For the multi-term models discussed in \sect{multiterm}, \citet{Palmer09}
presents an adaptation of the \citet{Press89} method that can compute the
multi-term result in $\mathcal{O}(NK\log N)$, for $N$ data points and
$K$ Fourier components.

All periodograms in this paper were computed using the Astropy
implementation of the \citet{Press89}, \citet{Zechmeister09}, and
\citet{Palmer09} algorithms, which was adapted from Python code originally
published by \citet{ICVG2014} and \citet{VanderPlas2015}.
All code for this paper is available in the form of Jupyter notebooks on the
author's GitHub repository\footnote{\url{http://github.com/jakevdp/PracticalLombScargle}}
